Seasonal Variation in Marriage License Applications

### 2024-09-27 paper/paper.qmd
variables of interest

# Introduction
Marriage decisions are often driven but just in terms of practicality, but in terms of deeply emotional and sometimes irrational impulses. Symbolic dates like Valentine's Day and Christmas play a key role in this. Even during unprecedented times like the COVID-19 pandemic, love and tradition lead people to marry at significant moments, despite the logistical nightmares these choices presented. This paper examines trends in marriage licenses issued in Toronto from 2011 to 2023, with a focus on seasonal periods like February and December.

@@

Marriage trends are a very good indicator of changes in society, reflecting broader shifts in demographics, economic circumstances, and changing cultural preferences. Understanding how external factors like seasonal holidays and different disruptions to the overall society influence marriage decisions can offer us valuable insights into human behavior and societal recovery. By identifying consistent seasonal patterns, this analysis can help wedding-retalted businesses (venues, caters, DJ's, etc.)anticipate periods of higher demand and better allocate resource. Additionally, civil centers can use this data to optimise staffing in order to increase efficiency.

@@

## Tools

We use @citeR and @opendata \* `ggplot2` [@citeggplot] \* `dplyr` [@citedplyr] \* `readr` [@citereadr] \* `tibble` [@citetibble]

## Variable Descriptions

@@

@@

```
```{r}
#| label: december-plot
#| fig-cap: "Figure 2: Total Marriage Licenses Issued in December (2011-2023)"
#| echo: false
#| warning: false
#| message: false

@@

```
## Civil Center Comparison

>>>>

# Introduction

Marriage decisions are often driven but just in terms of practicality, but in terms of deeply emotional and sometimes irrational impulses. Symbolic dates like Valentine's Day and Christmas play a key role in this. Even during unprecedented times like the COVID-19 pandemic, love and tradition lead people to marry at significant moments, despite the logistical nightmares these choices presented. This paper examines trends in marriage licenses issued in Toronto from 2011 to 2023, with a focus on seasonal periods like February and December.

@@

Marriage trends are a very good indicator of changes in society, reflecting broader shifts in demographics, economic circumstances, and changing cultural preferences. Understanding how external factors like seasonal holidays and different disruptions to the overall society influence marriage decisions can offer us valuable insights into human behavior and societal recovery. By identifying consistent seasonal patterns, this analysis can help wedding-retated businesses (venues, caters, DJ's, etc.)anticipate periods of higher demand and better allocate resource. Additionally, civil centers can use this data to optimise staffing in order to increase efficiency.

@@

The dataset for this report consist of statistics for marriage licence quantities by civic centre's in Toronto from 2011-2023. This data comes from `opendatatoronto`, a public repository that provides access to different civil datasets. These statistics were downloaded, cleaned, parsed, analysed, and visualised using R (@citeR), a statistical programming language, along with package support from `tidyverse` (@citetidyverse), various different libraries such as:

-   `ggplot2` [@citeggplot]
-   `dplyr` [@citedplyr]
-   `readr` [@citereadr]
-   `tibble` [@citetibble]

For further cleaning, the `janitor` (@citejanitor) package was used and the `knitr` was used too.

## Variables of Interest

@@

The dataset has 544 rows and 6 columns. Each row represents the number of marriage licenses issued at a civic center during a given month, along with a corresponding year and a constructed date column. @tbl-marriage-license-sample describes the variables included in the dataset. These variables include:

- `civic_centre` 
- `marriage_licenses`
- `year`
- `month`
- `date`

The data is organised by moth and aggregated for each civic center. While it would have been benefitial to have data at the daily level, the monthy data still allows for meaningful analysis of seasonal trends.

@@

```{r}
#| label: december-plot
#| fig-cap: "Figure 2: Total Marriage Licenses Issued in December (2011-2023)"
#| echo: false
#| warning: false
#| message: false

@@

## Civil Center Comparison
